Music adaptation: Analysis

### 2022-10-17 analysis/baseline.Rmd
export R script
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
correct errors for ptof category analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r}
ptof_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF" & Category == "both" | Subcomponent2 == "PtoF" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

ptof_ca_par_aov
pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```

>>>>

```{r}
ptof_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF" & Category == "both" | Subcomponent2 == "PtoF" & Category == "art_only" | Subcomponent2 == "PtoF" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

ptof_ca_par_aov
pairs(emmeans(ptof_ca_par_aov, "Category"), adjust = "tukey")
```

```{r export, include = FALSE}
knitr::purl("baseline.Rmd")
```
